Sampling Strategies in Decisions from Experience

### 2021-12-20 manuscript.Rmd
Update introduction

---
title             : "Sampling Strategies in Decisions from Experience: Property Representation and Probability Weighting Approximation"
shorttitle        : "Sampling strategies in decisions from experience"

@@

@@

Decision making is an information-processing problem whose solution requires a selection among choice alternatives. 
The basic structure of the problem may be modeled by the inclusion map $\iota : A' \mapsto A$, where $\iota(a) = a$ for all $a \in A'$, indicating that decision making is a *process* that starts from an initial set $A$, including all choice alternatives, and stops at a proper subset $A' \subset A$, including only the chosen alternatives. 
Given that the selection process is systematic---as opposed to random---the chosen alternatives in $A'$ should possess the same *property* or combination of several properties which the other alternatives in the complementary subset $A \setminus A'$ do not possess.
We may label the properties that serve to distinguish between the chosen and non-chosen alternatives as *selection criteria*.

>>>>

---
title             : "Sampling Strategies in Decisions from Experience: Property Representation and Probability Weighting Approximation"
shorttitle        : "Sampling strategies"

@@

<!-- Introduction -->

Any cognitive system operates on information inputs from an environment or memory. 
Often, however, these inputs do not readily describe the *properties* that the operating system uses to control the output. 
To obtain useful descriptions of the properties of interest, it is rather required to make inferences from incomplete or noisy inputs.
Since how the input is represented determines the information that is made explicit and the costs at which certain operations can be carried out on that information [@marrVisionComputationalInvestigation1982], the feasibility and ease of these inferences depends greatly on the choice of *representation*.
For example, probabilistic models of cognition suggest that a broad range of different assumptions about how people may structurally represent input information are required to capture their inferences about the extensions of novel properties in different inductive contexts [@griffithsProbabilisticModelsCognition2010; @kempStructuredStatisticalModels2009].
Hence, to explain the operations that turn an input into an output, one needs to understand the properties that control the output, the representation that is used by the cognitive system to describe these properties, and the costs of making the descriptions in that representation, including their susceptibility to distortions from noise or uncertainty.

@@

Decision making is an information-processing problem whose solution requires a selection among choice alternatives. 
The basic structure of the problem may be modeled by the inclusion map $\iota : A' \mapsto A$, where $\iota(a) = a$ for all $a \in A'$, indicating that decision making is a *process* that starts from an initial set $A$, including all choice alternatives, and stops at a proper subset $A' \subset A$, including only the chosen alternatives. 
Given that the selection process is systematic---as opposed to random---the chosen alternatives in $A'$ should possess the same property or combination of several properties which the other alternatives in the complementary subset $A \setminus A'$ do not possess.
We may label the properties that serve to distinguish between the chosen and non-chosen alternatives as *selection criteria*.
